A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-09 sections/model_overview/main.tex
Change some of the definitions

The queueing systems of the hospitals are designed in such a way where they can
accept two types
of individuals. 
Type 2 individuals are defined as non-urgent patients arriving in ambulances 
that are allocated by the ambulance service and 
type 1 individuals are individuals arriving from other sources 
(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
% TODO: Type 1 - type 2 definition defined on queueing section as well
Each hospital may then choose to block type 2 individuals 
when the hospital reaches a certain capacity. 
The strategy sets for each hospital is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of hospitals \(A\) and \(B\). We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

>>>>

The queueing systems of the hospitals are designed in such a way where they can
accept two types of individuals (section \ref{sec:queueing_model}). 
Each hospital may then choose to block type 2 individuals 
when the hospital reaches a certain capacity. 
The strategy sets for each hospital is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of hospitals \(A\) and \(B\). We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

### 2022-03-09 sections/queueing_model/blocking_time/main.tex
Minor changes on queueing section
Change some of the definitions

Here \(S_A^{(2)}\) is the set of accepting states of type 2 individuals (defined
in (\ref{eq:accepting_states_type_2})) and \(\mathcal{A}_i(u,v) \, i \in 
\{1, 2\} \) is the state that the model would go to when the system is at state 
\( (u,v) \) and a class \(i\) individual arrives.

>>>>

Here \(S_A^{(2)}\) is the set of accepting states of type 2 individuals (defined
in equation (\ref{eq:accepting_states_type_2})) and \(\mathcal{A}_i(u,v)\) for
\(i \in \{1, 2\} \) is the state that the system would go to when the system is
at state \( (u,v) \) and an individual of type \(i\) arrives.

### 2022-03-09 sections/queueing_model/main.tex
Change some of the definitions

\section{A queueing model for the ED-EMS interface}\label{sec:queueing_model}
% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queueing model that consists of two waiting zones; the parking space
and the hospital waiting space.

@@

The model consists of two types of individuals; type 1 and type 2.
% TODO: Decide whether to define type 1, 2 only in queueing section, only in game section, or both
Type 2 individuals are non-urgent patients arriving in ambulances (i.e. patients
in ambulances that would not be at risk if they were blocked at the parking 
space) and type 1 individuals are individuals arriving from other sources 
(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
Type 1 individuals arrive instantly at the hospital's waiting space and wait to
receive their service. 
Type 2 individuals arrive at the parking space and wait there until they are 
allowed to move to the hospital.
They are allowed to proceed only when the number of 
patients in the hospital is less than the
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
type 2 patients that arrive will stay 
\textit{blocked} in the parking space until the number of patients in 
the hospital falls below \(T\). 
This is shown diagrammatically in Figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

\begin{itemize}
    \item \(\lambda_i\): The arrival rate of individuals of type 
    \(i\in\{1, 2\}\)
    \item \(\mu\): The service rate for individuals receiving service
    \item \(C\): The number of servers
    \item \(T\): The threshold at which type 2 individuals are blocked
\end{itemize}

@@

Consequently, there are some additional performance measures of interest that
are not as straightforward to calculate.
Such performance measures are the mean waiting time in the system (for both 
type 1 and type 2 individuals), the mean time blocked in the parking space (only
valid for type 2 individuals) and the proportion of individuals in the hospital
whose waiting time falls within a predefined time target (for both types).
% TODO: Explain why these performance measures are needed? (for the game)

>>>>

\section{A queueing model for the ED-EMS interface}\label{sec:queueing_model}
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queueing model that consists of two waiting zones; the parking space
and the hospital waiting space.

@@

The model consists of two types of individuals; type 1 and type 2.
Type 2 individuals are patients arriving in ambulances who can be blocked 
(usually patients that are deemed not to be critical) 
and type 1 individuals are individuals arriving from other sources 
(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
Type 1 individuals arrive instantly at the hospital's waiting space and wait to
receive their service. 
Type 2 individuals arrive at the parking space and wait there until they are 
allowed to move to the hospital.
They are allowed to proceed only when the number of 
patients in the hospital is less than the
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
type 2 patients that arrive will stay 
\textit{blocked} in the parking space until the number of patients in 
the hospital falls below \(T\). 
This is shown diagrammatically in Figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

\begin{itemize}
    \item \(\lambda_i\): The arrival rate of individuals of type 
    \(i\in\{1, 2\}\)
    \item \(\mu\): The service rate for individuals receiving service
    \item \(C\): The number of servers (either healthcare professionals
    or available beds in the ED)
    \item \(T\): The threshold at which type 2 individuals are blocked
\end{itemize}

@@

Consequently, there are some additional performance measures of interest that
are not as straightforward to calculate.
Such performance measures are the mean waiting time in the system (for both 
type 1 and type 2 individuals), the mean time blocked in the parking space (only
valid for type 2 individuals) and the proportion of individuals in the hospital
whose waiting time falls within a predefined time target (for both types).
